Exploring approaches ro probablistic record linkage using similarity searching

### 2017-10-30 paper.tex
Update on Overleaf.

\section{approach section?}
\label{sec-overview}

>>>>

\section{Approach}
\label{sec-approach}

In this paper we explore the efficacy of the use of different similarity search algorithms in probabilistic record linkage. We explore two inexact algorithms: LSH and MIFile \cite{amato2014mi} one exact method: mTrees \cite{paolociaccia2m}. We also use a simple brute force exact technique as a baseline for comparison although this approach can only be applied to the smallest of our datasets.
